Dependent Object Types

### 2012-06-30 doc/semester/report.tex
wip: example

% TODO

>>>>

\subsection{Program Examples}

\begin{align*}
&\mlnew {\mi{root}} {\Top \mlrefine r {\\
&\ \Ldecl {\mi{Unit}} \Bot \Top\\
&\ \ldecl {\mi{unit}} {\Top \tfun {.\mi{Unit}}}\\
&\ \Ldecl {\mi{Boolean}} \Bot {\Top \mlrefine z {\\
&\ \gap \ldecl {\mi{ifNat}} {(r.\mi{Unit} \tfun r.\mi{Nat}) \tfun (r.\mi{Unit} \tfun r.\mi{Nat}) \tfun r.\mi{Nat}}\\
&\gap}}\\
&\ \ldecl {\mi{false}} {{r.\mi{Unit}} \tfun {r.\mi{Boolean}}}\\
&\ \ldecl {\mi{true}} {{r.\mi{Unit}} \tfun {r.\mi{Boolean}}}\\
&\ \Ldecl {\mi{Nat}} \Bot {\Top \mlrefine z {\\
&\ \gap \ldecl {\mi{isZero}} {r.\mi{Unit} \tfun r.\mi{Boolean}}\\
&\ \gap \ldecl {\mi{pred}} {r.\mi{Unit} \tfun r.\mi{Nat}}\\
&\ \gap \ldecl {\mi{succ}} {r.\mi{Unit} \tfun r.\mi{Nat}}\\
&\gap}}\\
&\ \ldecl {\mi{zero}} {{r.\mi{Unit}} \tfun {r.\mi{Nat}}}\\
&\ \ldecl {\mi{successor}} {{r.\mi{Nat}} \tfun {r.\mi{Nat}}}\\
&\ \ldecl {\mi{error}} {{r.\mi{Unit}} \tfun \Bot}\\
&}\mlldefs{\\\displaybreak[3]
&\ \mi{unit}  = \abs x \Top {\new u {\mi{root}.\mi{Unit}} u}\\
%
&\ \mi{false} = \abs u {\mi{root}.\mi{Unit}} {\\
&\ \gap \mlnew {\mi{ff}} {\mi{root}.\mi{Boolean} \mlldefs{\\
&\ \gap\gap {\mi{ifNat}} = \abs t {\mi{root}.\mi{Unit} \tfun \mi{root}.\mi{Nat}} {\abs e {\mi{root}.\mi{Unit} \tfun \mi{root}.\mi{Nat}}\\&\gap\gap\gap\app e {\mi{root}.\mi{unit}}}\\
&\ \gap}}{
\ \gap \mi{ff}}
&}\\
%
&\ \mi{true} = \abs u {\mi{root}.\mi{Unit}} {\\
&\ \gap \mlnew {\mi{t}} {\mi{root}.\mi{Boolean} \mlldefs{\\
&\ \gap\gap {\mi{ifNat}} = \abs t {\mi{root}.\mi{Unit} \tfun \mi{root}.\mi{Nat}} {\abs e {\mi{root}.\mi{Unit} \tfun \mi{root}.\mi{Nat}}\\&\gap\gap\gap\app t {\mi{root}.\mi{unit}}}\\
&\ \gap}}{
\ \gap \mi{tt}}
&}\\
%
&}}{
foo\\
&foo
}
\end{align*}
